### 2023-01-24 article3.qmd
update

Contrarily to previous works [@Estapa2013-gw; @Estapa2017-jr], we chose an empirical statistical approach instead of fixed thresholds to detect jumps. As a result, we firstly computed the slope between each point, then we computed the z-score (i.e. standard score) of each slope assuming a normal distribution of the latter. The detection of jumps thus consisted in spotting outliers in the z-score distribution. For this, we computed the interquartile range ($IQR$) between the first ($Q_{1}$) and third ($Q_{3}$) quartiles. Positive and negative jumps were defined as, respectively, a z-score above $Q_{3} + 1.5 \times IQR$ and below $Q_{1} - 1.5 \times IQR$. We found that this method better detected outliers than the one used to despike the $c_{p}$ signal.

@@

We used the same relationship to compute $F_{big}$ was replacing $slope_{w}$ as the sum of positive jumps (negative jumps were disgarded) divided by the drifting time.

@@

$F_{big}$ was estimated at 200 m between 0 (no deposition of big particles on the transmissometer window) and `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$max_bigf, 1)` mg C m$^{-2}$ day$^{-1}$ with an average of `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$mean_bigf, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$std_bigf, 1)` mg C m$^{-2}$ day$^{-1}$. High fluxes (\> 100 mg C m$^{-2}$ day$^{-1}$) were measured by 3 out of 4 floats at the end of May before a sharp decrease towards July. At 500 m, $F_{big}$ ranges between `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$min_bigf, 1)` mg C m$^{-2}$ day$^{-1}$ and `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$max_bigf, 1)` mg C m$^{-2}$ day$^{-1}$ with an average of `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$mean_bigf, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$std_bigf, 1)` mg C m$^{-2}$ day$^{-1}$, decreasing from September to January. At 1000 m, $F_{big}$ shows a similar pattern than the one observed for $F_{small}$ with an increase from June to mid-JulyAugust, followed by a decrease towards January, with values ranging from 0 to `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$max_bigf, 1)` mg C m$^{-2}$ day$^{-1}$ with an average of `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$mean_bigf, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$std_bigf, 1)` mg C m$^{-2}$ day$^{-1}$.

>>>>

Contrarily to previous works [@Estapa2013-gw; @Estapa2017-jr], we chose an empirical statistical approach instead of fixed thresholds to detect jumps. As a result, we firstly computed the slope between each point, then we computed the z-score (i.e. standard score) of each slope, that follows a normal distribution. The detection of jumps thus consisted in spotting outliers in the z-score distribution. For this, we computed the interquartile range ($IQR$) between the first ($Q_{1}$) and third ($Q_{3}$) quartiles. Positive and negative jumps were defined as, respectively, a z-score above $Q_{3} + 1.5 \times IQR$ and below $Q_{1} - 1.5 \times IQR$. We found that this method better detected outliers than the one used to despike the $c_{p}$ signal.

@@

We used the same relationship to compute $F_{big}$ by replacing $slope_{w}$ as the sum of positive jumps (negative jumps were discarded) divided by the drifting time.

@@

$F_{big}$ was estimated at 200 m between 0 (no deposition of big particles on the transmissometer window) and `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$max_bigf, 1)` mg C m$^{-2}$ day$^{-1}$ with an average of `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$mean_bigf, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$std_bigf, 1)` mg C m$^{-2}$ day$^{-1}$. High fluxes (\> 100 mg C m$^{-2}$ day$^{-1}$) were measured by 3 out of 4 floats at the end of May before a sharp decrease towards July. At 500 m, $F_{big}$ ranges between `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$min_bigf, 1)` mg C m$^{-2}$ day$^{-1}$ and `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$max_bigf, 1)` mg C m$^{-2}$ day$^{-1}$ with an average of `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$mean_bigf, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$std_bigf, 1)` mg C m$^{-2}$ day$^{-1}$, decreasing from September to January. At 1000 m, $F_{big}$ shows a similar pattern than the one observed for $F_{small}$ with an increase from June to mid-July, followed by a decrease towards January, with values ranging from 0 to `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$max_bigf, 1)` mg C m$^{-2}$ day$^{-1}$ with an average of `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$mean_bigf, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$std_bigf, 1)` mg C m$^{-2}$ day$^{-1}$.
